\thetitle

### 2022-06-13 paper/paper.tex
small korean typo
"array" instead of "list"

\ifen
Finally, we remark that the objective function of \eqref{headlineproblem} is a nondecreasing submodular function. However, our research employs more elementary analytical techniques, and our approximation results are tighter than those associated with generic submodular maximization algorithms. For example, a well-known result of Fisher et al. (1978) implies that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for the $g_j = 1$ case of the college application problem, whereas we show that the same algorithm is exact. As for the general problem, an equivalent approximation ratio is achievable when maximizing a submodular set function over a knapsack constraint using a variety of relaxation techniques (Badanidiyuru and Vondrák 2014; Kulik et al. 2013). Indeed, $1 - 1/e$ is the highest approximation coefficient achievable by a polynomial-time algorithm for this problem (Nemhauser and Wolsey 1978). But in the college application problem, the existence of the FPTAS supersedes these results.
\else
마지막으로, \eqref{headlineproblem}의 목적함수는 submodular하며 단조 증가하는 함수이다. 그런데, 본 연구는 더 기초적인 분석 기술을 이용하며, 일반적인 submodular 최대화 알고리즘보다 좋은 근사 계수를 얻게 된다. 예를 들어 Fisher 외 (1978)의 잘 알려진 결과에 따라, 대학 지원 문제의 $g_j = 1$인 경우에서 탐욕 해법의 점근적 근사 계수가 $(1 - 1/e)$이 되며, 본 논문에서 같은 해법이 정확함을 보인다. 일반적인 문제에 대해서는, 배낭 제약식 위에서 submodular 집합 함수를 최대하는 문제에서, 다양한 완화 기술을 활용하면 거의 동등한 근사 계수를 이뤄 낼 수 있다 (Badanidiyuru and Vondrák 2014; Kulik et al. 2013). 이 문제를 위한 다항 시간 해법은 $1 - 1/e$보다 좋은 근사 계수를 가질 수 없음이 알려져 있다 (Nemhauser and Wolsey 1978). 그러나 대학 지원 문제에서, FPTAS의 존재성은 그보다 강한 결과이다.
\fi

@@

\ifen 
We reduce the computation time to $O(hm)$ by taking advantage of the transformation from Lemma \ref{eliminationtheorem}. Once school $k$ is added to $\mathcal{X}$, we eliminate it from the set $\mathcal{C}\setminus \mathcal{X}$ of candidates, and update the $t_j$-values of the remaining schools according to \eqref{howtotransformtj}. Now, the \emph{next} school added must be the optimal singleton portfolio in the modified market. But the optimal singleton portfolio consists simply of the school with the highest value of $f_j \bar t_j$. Therefore, by updating the $t_j$-values at each iteration according to \eqref{howtotransformtj}, we eliminate the need to compute $v(\mathcal{X})$ entirely. Moreover, this algorithm does not require the schools to be indexed in ascending order by $t_j$, which removes the $O(m\log m)$ sorting cost.
\else
기본 정리 \ref{eliminationtheorem}에서 제시한 변환을 활용하면 계산 시간을 $O(hm)$으로 감소시킬 수 있다. $\mathcal{X}$에 $k$를 추가하면, 후보자 집합인 $\mathcal{C}\setminus \mathcal{X}$에서 $k$를 소거하고 남은 학교의 $t_j$-값을 \eqref{howtotransformtj}에 따라 수정한다. 그러면 다음으로 추가하는 학교는 수정된 시장의 최적 단일 원소 포트폴리오가 되어야 한다. 그런데 최적 단일 원소 포트폴리오는 단순히 $f_j \bar t_j$가 가장 큰 학교로 이루어진다. 따라서 각 반복 단계에서 \eqref{howtotransformtj}을(를) 이용하여 $t_j$-값을 수정하면 $v(\mathcal{X})$를 계산할 필요가 완전히 없어진다. 게다가 이 알고리즘에서 $t_j$를 배열할 필요가 없으므로 $O(m\log m)$인 배열 비용이 사라진다. \fi
\ifen
Algorithm \ref{algorithmforlargeh} outputs a list $\mathtt{X}$ of the $h$ schools to which Alma should apply. The schools appear in the order of entry such that when the algorithm is run with $h=m$, the optimal portfolio of size $h$ is given by $\mathcal{X}_h = \{\mathtt{X[1]}, \dots, \mathtt{X[h]}\}$. The entries of the list $\mathtt{V}$ give the valuation thereof. 
\else
알고리즘 \ref{algorithmforlargeh}은(는) 알마가 지원하는 $h$개의 학교를 목록 $\mathtt{X}$로 출력한다. 그의 원소들은 진입하는 순서대로 등장한다. 즉, $h=m$으로 알고리즘을 돌리면 크기가 $h$인 최적 포트폴리오는 $\mathcal{X}_h = \{\mathtt{X[1]}, \dots, \mathtt{X[h]}\}$와 같다. 또한 목록 $\mathtt{V}$의 원소들은 해당 포트폴리오의 가치다. \fi

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Optimal portfolio algorithm for Alma’s problem.} \label{algorithmforlargeh}
\KwIn{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application limit $h \leq m$.}
%Index schools in ascending order by $t$\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ empty lists\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\operatorname{append!}(\mathtt{X}, k)$\;
     \lIfElse{$i=1$}{$\operatorname{append!}(\mathtt{V}, f_k t_k)$}
     {$\operatorname{append!}(\mathtt{V}, \mathtt{V[i-1]} + f_k t_k)$}
    \For{$j \in \mathcal{C}$}
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \else {
\begin{algorithm}[H] 
%\DontPrintSemicolon
\caption{알마의 문제를 위한 최적 포트폴리오 알고리즘.} \label{algorithmforlargeh}
\KwIn{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 제한 $h \leq m$.}
%$t$의 순서대로 학교의 지표를 짓는다\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ 빈 목록\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\operatorname{append!}(\mathtt{X}, k)$\;
     \lIfElse{$i=1$}{$\operatorname{append!}(\mathtt{V}, f_k t_k)$}
     {$\operatorname{append!}(\mathtt{V}, \mathtt{V[i-1]} + f_k t_k)$}
    \For{$j \in \mathcal{C}$} 
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \fi

\begin{theorem}[\ifen Validity of Algorithm \ref{algorithmforlargeh}\else 알고리즘 \ref{algorithmforlargeh}의 타당성\fi] \label{validityofalmaalgorithm}
\ifen Algorithm \ref{algorithmforlargeh} produces an optimal application portfolio for Alma's problem in $O(h m)$ time.
\else 알고리즘 \ref{algorithmforlargeh}은(는) $O(h m)$ 시간에 알마의 문제를 위한 최적 지원 포트폴리오를 출력한다.\fi
\end{theorem}
\begin{proof}
\ifen
Optimality follows from the proof of Theorem \ref{nestedapplication}. Suppose $\mathcal{C}$ is stored as a list. Then at each of the $h$ iterations of the main loop, finding the top school costs $O(m)$, and the $t_j$-values of the remaining $O(m)$ schools are each updated in unit time. Therefore, the overall time complexity is $O(h m)$.
\else
최적성은 정리 \ref{nestedapplication}의 증명에 따라 성립한다. $\mathcal{C}$를 목록 구현으로 저장한다고 하자. 그러면 각 $h$개의 반복 단계에서 최적 추가 학교를 구하는 시간은 $O(m)$이며 나머지 $O(m)$개 학교의 $t_j$-값을 각 단위 시간으로 수정할 수 있다. 따라서 전체 시간 복잡도가 $O(h m)$이다.
\fi
\end{proof}

\ifen 
It is possible to store $\mathcal{C}$ as a binary max heap rather than a list. The heap is ordered according to the criterion $i \geq j \iff f_i t_i \geq f_j t_j$, and by draining the heap and reheapifying at the end of each iteration, the computation time remains $O(hm)$. However, in our numerical experiments, whose results are reported in Section \ref{numericalexperiments},
we found the list implementation to be much faster, because it is possible to identify the entering school $k$ as the utility parameters are updated, which all but eliminates the cost of the $\argmax\{\}$ operation. 
\else
$\mathcal{C}$는 목록 대신 이진 최대 힙 구현으로 저장하는 방법도 고려한다. 단, 힙의 순서는 $i \geq j \iff f_i t_i \geq f_j t_j$의 조건으로 정의하며, 각 반복 단계의 마지막 단계에서 힙을 비우고 다시 힙화(heapify)하면 $O(hm)$ 계산 시간을 유지할 수 있다. 그러나 (\ref{numericalexperiments}절에서 결과를 제시할) 수리 실험에서 목록 구현으로 구성한 알고리즘이 더 빨랐다. 효용 모수를 수정하면서 $k$를 구함으로 $\argmax\{\}$ 연산의 계산 비용을 거의 제거할 수 있기 때문이다.
\fi

@@

\ifen \subsection{Summary of results} \else \subsection{결과 정리}\fi
\ifen
Experiment 1 compared the performance of Algorithm \ref{algorithmforlargeh} for homogeneous-cost markets of various sizes when the set of candidate schools $\mathcal{C}$ is stored as a list and as a binary max heap ordered by the $f_j \bar t_j$-values. The results appear in Table \ref{experiment1results}. Our results indicate that the list implementation is faster. %However, the ratio between the average times of the two implementations stays roughly constant, suggesting that a more effective heap implementation could be competitive in certain classes of problem instances. Overall, the rate of growth is quadratic in $m$, which accords with the $O(hm)$ time complexity result of Theorem \ref{validityofalmaalgorithm}.
\else
실험 1에서, 동일한 지원 비용으로 정의된 크기가 다양한 시장에 대해 알고리즘 \ref{algorithmforlargeh}의 성능을 고려했다. 이를 $\mathcal{C}$를 목록 혹은 $f_j \bar t_j$-값에 따라 배열된 힙 구현으로 구성하는 경우로 나눴으며 실험 결과는 표 \ref{experiment1results}에서 등장한다. 실험 결과에 따라 목록 구현이 더 빠른 해법이었다. %그러나, 두개의 방법 사이에 계산 시간 비율은 거의 상수이므로 개선된 힙 해법이 어떤 문제 인스턴스에 대해 더 빠를 가능성이 있어 보인다. 전체적으로 계산 시간은 $m$의 제곱으로 늘아나며 이는 정리 \ref{validityofalmaalgorithm}에서 말한 $O(hm)$ 시간과 동의한다.
\fi

%\ifen
%In our first experiment, we compare the performance of Algorithm \ref{algorithmforlargeh} for homogeneous-cost markets of various sizes when the set of candidate schools $\mathcal{C}$ is stored as a list and as a binary max heap ordered by the $f_j \bar t_j$-values. The results appear in Table \ref{experiment1results}. Our results indicate that the heap implementation is faster. Overall, the rate of growth is quadratic in $m$, which accords with the $O(hm)$ time complexity result of Theorem \ref{validityofalmaalgorithm}.
%\else
%첫 번째 실험에서, 동일한 지원 비용으로 정의된 크기가 다양한 시장에 대해 알고리즘 \ref{algorithmforlargeh}의 성능을 고려했다. 이를 $\mathcal{C}$를 목록 혹은 $f_j \bar t_j$-값에 따라 배열된 힙 구현으로 구성하는 경우로 나눴으며 실험 결과는 표 \ref{experiment1results}에서 등장한다. 실험 결과에 따라 힙 구현이 더 빠른 해법이었다. 전체적으로 계산 시간은 $m$의 제곱으로 늘아나며 이는 정리 \ref{validityofalmaalgorithm}에서 말한 $O(hm)$ 시간과 동의한다.
%\fi

@@

\begin{table}[h!] \centering
\small
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with list\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(목록 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &    0.00 &  (0.00) &    0.01 &    (0.00) \\
    64 &    0.01 &  (0.00) &    0.08 &    (0.02) \\
   256 &    0.06 &  (0.00) &    0.96 &    (0.26) \\
  1024 &    0.82 &  (0.03) &   14.27 &    (2.28) \\
  4096 &   12.87 &  (0.71) &  230.77 &   (18.75) \\
 16384 &  199.48 &  (1.77) & 3999.19 &  (283.48)
\end{tabular}
\caption{\label{experiment1results} \normalsize
\ifen (Experiment 1.) Time in ms to compute an optimal portfolio for an admissions market with homogeneous application costs using Algorithm \ref{algorithmforlargeh} when $\mathcal{C}$ is stored as a list and as a heap. \lastptofcaption~In every case, $h = m/2$. 
\else (실험 1.) 단위: ms. 알고리즘 \ref{algorithmforlargeh}에서 $\mathcal{C}$를 목록 또는 힙 구현으로 저장했을 때, 
동일 지원 비용 입학 시장의 최적 지원 포트폴리오를 계산하는 시간. \lastptofcaption~모든 경우, $h = m/2$. \fi}
\end{table}

>>>>

\ifen
Finally, we remark that the objective function of \eqref{headlineproblem} is a nondecreasing submodular function. However, our research employs more elementary analytical techniques, and our approximation results are tighter than those associated with generic submodular maximization algorithms. For example, a well-known result of Fisher et al. (1978) implies that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for the $g_j = 1$ case of the college application problem, whereas we show that the same algorithm is exact. As for the general problem, an equivalent approximation ratio is achievable when maximizing a submodular set function over a knapsack constraint using a variety of relaxation techniques (Badanidiyuru and Vondrák 2014; Kulik et al. 2013). Indeed, $1 - 1/e$ is the highest approximation coefficient achievable by a polynomial-time algorithm for this problem (Nemhauser and Wolsey 1978). But in the college application problem, the existence of the FPTAS supersedes these results.
\else
마지막으로, \eqref{headlineproblem}의 목적함수는 submodular하며 단조 증가하는 함수이다. 그런데, 본 연구는 더 기초적인 분석 기술을 이용하며, 일반적인 submodular 최대화 알고리즘보다 좋은 근사 계수를 얻게 된다. 예를 들어 Fisher 외 (1978)의 잘 알려진 결과에 따라, 대학 지원 문제의 $g_j = 1$인 경우에서 탐욕 해법의 점근적 근사 계수가 $(1 - 1/e)$이 되며, 본 논문에서 같은 해법이 정확함을 보인다. 일반적인 문제에 대해서는, 배낭 제약식 위에서 submodular 집합 함수를 최대하는 문제에서, 다양한 완화 기술을 활용하면 거의 동등한 근사 계수를 이뤄 낼 수 있다 (Badanidiyuru and Vondrák 2014; Kulik et al. 2013). 이 문제를 위한 다항 시간 해법은 $1 - 1/e$보다 좋은 근사 계수를 가질 수 없음이 알려져 있다 (Nemhauser와 Wolsey 1978). 그러나 대학 지원 문제에서, FPTAS의 존재성은 그보다 강한 결과이다.
\fi

@@

\ifen 
We reduce the computation time to $O(hm)$ by taking advantage of the transformation from Lemma \ref{eliminationtheorem}. Once school $k$ is added to $\mathcal{X}$, we eliminate it from the set $\mathcal{C}\setminus \mathcal{X}$ of candidates, and update the $t_j$-values of the remaining schools according to \eqref{howtotransformtj}. Now, the \emph{next} school added must be the optimal singleton portfolio in the modified market. But the optimal singleton portfolio consists simply of the school with the highest value of $f_j \bar t_j$. Therefore, by updating the $t_j$-values at each iteration according to \eqref{howtotransformtj}, we eliminate the need to compute $v(\mathcal{X})$ entirely. Moreover, this algorithm does not require the schools to be indexed in ascending order by $t_j$, which removes the $O(m\log m)$ sorting cost.
\else
기본 정리 \ref{eliminationtheorem}에서 제시한 변환을 활용하면 계산 시간을 $O(hm)$으로 감소시킬 수 있다. $\mathcal{X}$에 $k$를 추가하면, 후보자 집합인 $\mathcal{C}\setminus \mathcal{X}$에서 $k$를 소거하고 남은 학교의 $t_j$-값을 \eqref{howtotransformtj}에 따라 수정한다. 그러면 다음으로 추가하는 학교는 수정된 시장의 최적 단일 원소 포트폴리오가 되어야 한다. 그런데 최적 단일 원소 포트폴리오는 단순히 $f_j \bar t_j$가 가장 큰 학교로 이루어진다. 따라서 각 반복 단계에서 \eqref{howtotransformtj}을(를) 이용하여 $t_j$-값을 수정하면 $v(\mathcal{X})$를 계산할 필요가 완전히 없어진다. 게다가 이 알고리즘에서 $t_j$를 배열할 필요가 없으므로 $O(m\log m)$인 배열 비용이 사라진다. \fi
\ifen
Algorithm \ref{algorithmforlargeh} outputs an array $\mathtt{X}$ of the $h$ schools to which Alma should apply. The schools appear in the order of entry such that when the algorithm is run with $h=m$, the optimal portfolio of size $h$ is given by $\mathcal{X}_h = \{\mathtt{X[1]}, \dots, \mathtt{X[h]}\}$. The entries of the array $\mathtt{V}$ give the valuation thereof. 
\else
알고리즘 \ref{algorithmforlargeh}은(는) 알마가 지원하는 $h$개의 학교를 배열(array) $\mathtt{X}$로 출력한다. 그의 원소들은 진입하는 순서대로 등장한다. 즉, $h=m$으로 알고리즘을 돌리면 크기가 $h$인 최적 포트폴리오는 $\mathcal{X}_h = \{\mathtt{X[1]}, \dots, \mathtt{X[h]}\}$와 같다. 또한 배열 $\mathtt{V}$의 원소들은 해당 포트폴리오의 가치다. \fi

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Optimal portfolio algorithm for Alma’s problem.} \label{algorithmforlargeh}
\KwIn{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application limit $h \leq m$.}
%Index schools in ascending order by $t$\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ empty $h$-arrays\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\mathtt{X}[i] \gets k$\;
     \lIfElse{$i=1$}{$\mathtt{V}[i] \gets f_k t_k$}
     {$\mathtt{V}[i] \gets \mathtt{V}[i-1] + f_k t_k$}
    \For{$j \in \mathcal{C}$}
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \else {
\begin{algorithm}[H] 
%\DontPrintSemicolon
\caption{알마의 문제를 위한 최적 포트폴리오 알고리즘.} \label{algorithmforlargeh}
\KwIn{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 제한 $h \leq m$.}
%$t$의 순서대로 학교의 지표를 짓는다\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ 빈 $h$-배열\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\mathtt{X}[i] \gets k$\;
     \lIfElse{$i=1$}{$\mathtt{V}[i] \gets f_k t_k$}
     {$\mathtt{V}[i] \gets \mathtt{V}[i-1] + f_k t_k$}
    \For{$j \in \mathcal{C}$}
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \fi

\begin{theorem}[\ifen Validity of Algorithm \ref{algorithmforlargeh}\else 알고리즘 \ref{algorithmforlargeh}의 타당성\fi] \label{validityofalmaalgorithm}
\ifen Algorithm \ref{algorithmforlargeh} produces an optimal application portfolio for Alma's problem in $O(h m)$ time.
\else 알고리즘 \ref{algorithmforlargeh}은(는) $O(h m)$ 시간에 알마의 문제를 위한 최적 지원 포트폴리오를 출력한다.\fi
\end{theorem}
\begin{proof}
\ifen
Optimality follows from the proof of Theorem \ref{nestedapplication}. At each of the $h$ iterations of the main loop, finding the top school costs $O(m)$, and the $t_j$-values of the remaining $O(m)$ schools are each updated in unit time. Therefore, the overall time complexity is $O(h m)$.
\else
최적성은 정리 \ref{nestedapplication}의 증명에 따라 성립한다. 각 $h$개의 반복 단계에서 최적 추가 학교를 구하는 시간은 $O(m)$이며 나머지 $O(m)$개 학교의 $t_j$-값을 각 단위 시간으로 수정할 수 있다. 따라서 전체 시간 복잡도가 $O(h m)$이다.
\fi
\end{proof}

\ifen 
It is possible to store $\mathcal{C}$ as a binary max heap rather than an array. The heap is ordered according to the criterion $i \geq j \iff f_i t_i \geq f_j t_j$, and by draining the heap and reheapifying at the end of each iteration, the computation time remains $O(hm)$. However, in our numerical experiments, whose results are reported in Section \ref{numericalexperiments},
we found the array implementation to be much faster, because it is possible to identify the entering school $k$ as the utility parameters are updated, which all but eliminates the cost of the $\argmax\{\}$ operation. 
\else
$\mathcal{C}$는 배열 대신 이진 최대 힙 구현으로 저장하는 방법도 고려한다. 단, 힙의 순서는 $i \geq j \iff f_i t_i \geq f_j t_j$의 조건으로 정의하며, 각 반복 단계의 마지막 단계에서 힙을 비우고 다시 힙화(heapify)하면 $O(hm)$ 계산 시간을 유지할 수 있다. 그러나 (\ref{numericalexperiments}절에서 결과를 제시할) 수리 실험에서 배열 구현으로 구성한 알고리즘이 더 빨랐다. 효용 모수를 수정하면서 $k$를 구함으로 $\argmax\{\}$ 연산의 계산 비용을 거의 제거할 수 있기 때문이다.
\fi

@@

\ifen \subsection{Summary of results} \else \subsection{결과 정리}\fi
\ifen
Experiment 1 compared the performance of Algorithm \ref{algorithmforlargeh} for homogeneous-cost markets of various sizes when the set of candidate schools $\mathcal{C}$ is stored as an array and as a binary max heap ordered by the $f_j \bar t_j$-values. The results appear in Table \ref{experiment1results}. Our results indicate that the array implementation is faster. %However, the ratio between the average times of the two implementations stays roughly constant, suggesting that a more effective heap implementation could be competitive in certain classes of problem instances. Overall, the rate of growth is quadratic in $m$, which accords with the $O(hm)$ time complexity result of Theorem \ref{validityofalmaalgorithm}.
\else
실험 1에서, 동일한 지원 비용으로 정의된 크기가 다양한 시장에 대해 알고리즘 \ref{algorithmforlargeh}의 성능을 고려했다. 이를 $\mathcal{C}$를 배열 혹은 $f_j \bar t_j$-값에 따라 배열된 힙 구현으로 구성하는 경우로 나눴으며 실험 결과는 표 \ref{experiment1results}에서 등장한다. 실험 결과에 따라 배열 구현이 더 빠른 해법이었다. %그러나, 두개의 방법 사이에 계산 시간 비율은 거의 상수이므로 개선된 힙 해법이 어떤 문제 인스턴스에 대해 더 빠를 가능성이 있어 보인다. 전체적으로 계산 시간은 $m$의 제곱으로 늘아나며 이는 정리 \ref{validityofalmaalgorithm}에서 말한 $O(hm)$ 시간과 동의한다.
\fi

@@

\begin{table}[h!] \centering
\small
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with array\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(배열 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &    0.00 &  (0.00) &    0.01 &    (0.00) \\
    64 &    0.01 &  (0.00) &    0.08 &    (0.02) \\
   256 &    0.06 &  (0.00) &    0.96 &    (0.26) \\
  1024 &    0.82 &  (0.03) &   14.27 &    (2.28) \\
  4096 &   12.87 &  (0.71) &  230.77 &   (18.75) \\
 16384 &  199.48 &  (1.77) & 3999.19 &  (283.48)
\end{tabular}
\caption{\label{experiment1results} \normalsize
\ifen (Experiment 1.) Time in ms to compute an optimal portfolio for an admissions market with homogeneous application costs using Algorithm \ref{algorithmforlargeh} when $\mathcal{C}$ is stored as an array and as a heap. \lastptofcaption~In every case, $h = m/2$. 
\else (실험 1.) 단위: ms. 알고리즘 \ref{algorithmforlargeh}에서 $\mathcal{C}$를 배열 또는 힙 구현으로 저장했을 때, 
동일 지원 비용 입학 시장의 최적 지원 포트폴리오를 계산하는 시간. \lastptofcaption~모든 경우, $h = m/2$. \fi}
\end{table}
